The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-01-03 borel-regularity.tex
Remove revision coloring

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Phi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Definition~\ref{def:H_hat}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}[also \ref{re:thm:soln_is_Borel_sum}]\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\begin{corollary}[also \ref{re:cor:soln_borel-reg}]\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

The Poincar\'{e} solutions and the M.A.E.T. have inspired several other methods for solving linear level~1 ODEs. The ones we will discuss in this section are summarized in the following table. We classify solution methods by two features: whether the solutions they produce are analytic functions or formal series, and whether they solve the original equation on the frequency domain or an equivalent equation in the position domain.
\begin{center}
\begin{tabular}{l|l|l}
& \textbf{Analytic} & \textbf{Formal} \\ \hline
\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
\textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
& Fixed-point iteration~\cite{reg-sing-volterra} \\
\end{tabular}
\end{center}
%
\subsubsection{The Poincar\'{e} method and Borel summation}\label{sec:Poincare method}
%
An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$. These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve. The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} \colon P(-\alpha) = 0\}$. Poincar\'{e} guesses that each approximate solution $e^{-\alpha z}$ can be turned into an exact solution $e^{-\alpha z} \series{F}_\alpha$ using a formal correction factor $\series{F}_\alpha \in z^{-\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$. When $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$, the correction factor can be found order by order, starting from any chosen constant term. We will refer to the resulting solutions $e^{-\alpha z} \series{F}_\alpha \in e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ as Poincar\'{e}'s formal solutions.

@@

%\color{orange}
%\subsubsection{Action on power series with fractional exponents}
%\color{black}

@@

From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined. \begin{todo}[Transition text]\end{todo}

@@

Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace

@@

When we take the Borel sum of $\series{\Psi}_\alpha$, we start by retracing the construction steps described above. The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$, and summation then inverts the Taylor expansion, bringing us back to $\psi_\alpha$. We finish the Borel summation by taking the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$, giving $\Psi_\alpha$ by definition.
\end{proof}
\begin{todo}[Add flavor text]\end{todo}
\begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
\end{corollary}
\begin{proof}
In the proof of Theorem~\ref{re:thm:soln_is_Borel_sum}, we showed that the position-domain solution $\psi_\alpha \in \singexpalg{\tau_\alpha-1}(\Upsilon)$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$. Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi}_\alpha$ is the formal Laplace transform of $\series{\psi}_\alpha$, Lemma~\ref{lem:laplace-bridge} tells us that $\Psi_\alpha$ is asymptotic to $\series{\Psi}_\alpha$. Taking the Borel sum of $\series{\Psi}_\alpha$ gives us back $\Psi_\alpha$, by construction, so $\Psi_\alpha$ is Borel regular.
\end{proof}
%
\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
%
In~\cite{int-irreg}, Poincar\'{e} described a formal way to solve the equation $\mathcal{P}\series{\Phi} = 0$ for an operator of the form~\eqref{eqn:operator-P}. Choose a root $-\alpha$ of $P$, set $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$. Once the leading coefficient of $\series{\Psi}_\alpha$ is chosen, the rest of the coefficients are determined, and can be found order by order. The Ramis Index Theorem guarantees that $\series{\Psi}_\alpha$ will be $1$-Gevrey~\cite{ramis_index}.

We have come this far in our discussion of Poincar\'{e}'s method through formal reasoning in the frequency domain. From here, there are various ways to show that $\series{\Psi}_\alpha$ is Borel summable. We do it by using Theorem~4 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
\begin{theorem}\label{thm:summability_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
\end{theorem}
\begin{proof}
By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator \eqref{eq:hat_P}. By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$. Since the integrals in $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha$ converge absolutely, $\hat{\psi}_\alpha$ satisfies the same equation that its Taylor series does: $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0$.

>>>>

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}. equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$ where $\tau_\alpha$ is real and positive. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Phi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Definition~\ref{def:H_hat}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}[also \ref{re:thm:soln_is_Borel_sum}]\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\begin{corollary}[also \ref{re:cor:soln_borel-reg}]\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

The Poincar\'{e} solutions and the M.A.E.T. have inspired several other methods for solving linear level~1 ODEs. The ones we will discuss in this section are summarized in the following table. We classify solution methods by two features: whether the solutions they produce are analytic functions or formal series, and whether they solve the original equation on the frequency domain or an equivalent equation in the position domain.
\begin{center}
\begin{tabular}{l|l|l}
& \textbf{Analytic} & \textbf{Formal} \\ \hline
\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
\textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
& Fixed-point iteration~\cite{reg-sing-volterra} \\
\end{tabular}
\end{center}
%
\subsubsection{The Poincar\'{e} method and Borel summation}\label{sec:Poincare method}
%
An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ indexed by the roots $-\alpha$ of $P$, where $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$. These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve. The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} : P(-\alpha) = 0\}$. Poincar\'{e} guesses that each approximate solution $e^{-\alpha z}$ can be turned into an exact solution $e^{-\alpha z} \series{F}_\alpha$ using a formal correction factor $\series{F}_\alpha \in z^{-\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$. The correction factor can be found order by order, starting from any chosen constant term. We will refer to the resulting solutions $e^{-\alpha z} \series{F}_\alpha \in e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ as Poincar\'{e}'s formal solutions.

@@

@@

and define the constant $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$. From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined. \begin{todo}[Transition text]\end{todo}

@@

Choose a root $-\alpha$ of $P$ where $\tau_\alpha$ is real and positive. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace

@@

When we take the Borel sum of $\series{\Psi}_\alpha$, we start by retracing the construction steps described above. The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$, and summation then inverts the Taylor expansion, bringing us back to $\psi_\alpha$. We finish the Borel summation by taking the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$, giving $\Psi_\alpha$ by definition.
\end{proof}
\begin{todo}[Add flavor text]\end{todo}
\begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
\end{corollary}
\begin{proof}
In the proof of Theorem~\ref{re:thm:soln_is_Borel_sum}, we showed that the position-domain solution $\psi_\alpha \in \singexpalg{\tau_\alpha-1}(\Upsilon)$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$. Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi}_\alpha$ is the formal Laplace transform of $\series{\psi}_\alpha$, Lemma~\ref{lem:laplace-bridge} tells us that $\Psi_\alpha$ is asymptotic to $\series{\Psi}_\alpha$. Taking the Borel sum of $\series{\Psi}_\alpha$ gives us back $\Psi_\alpha$, by construction, so $\Psi_\alpha$ is Borel regular.
\end{proof}
%
\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
%
In~\cite{int-irreg}, Poincar\'{e} described a formal way to solve the equation $\mathcal{P}\series{\Phi} = 0$ for an operator of the form~\eqref{eqn:operator-P}. Choose a root $-\alpha$ of $P$ and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$, recalling that $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$. Once the leading coefficient of $\series{\Psi}_\alpha$ is chosen, the rest of the coefficients are determined, and can be found order by order. The Ramis Index Theorem guarantees that $\series{\Psi}_\alpha$ will be $1$-Gevrey~\cite{ramis_index}.

We have come this far in our discussion of Poincar\'{e}'s method through formal reasoning in the frequency domain. From here, there are various ways to show that $\series{\Psi}_\alpha$ is Borel summable. We do it by using Theorem~4 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
\begin{theorem}\label{thm:summability_ODE}
Choose a root $-\alpha$ of $P$ where $\tau_\alpha$ is real and positive. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
\end{theorem}
\begin{proof}
By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator \eqref{eq:hat_P}. By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$. Since the integrals in $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha$ converge absolutely, $\hat{\psi}_\alpha$ satisfies the same equation that its Taylor series does: $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0$.
